Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-16 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

There are various different integral defined for IVPMs, and the most
famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable
with $x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $\bar{\mu}:\events\rightarrow\mathscr{I}$
a classical IVPM such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ ,}\label{eq:interval-expectation}
\end{equation}
where 
\begin{equation} 
x[l,r]=\cases{ 
[xl,xr] & for $x\ge0$ ;\\
[xr,xl] & for $x\le0$ .
}
\end{equation}
Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
can be considered as weighted average of the possible outcomes of
$X$ as well, despite the ``weight''
\[
\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
\]
is tighter than the interval-valued probability of the corresponding
event. Since only one event can happen at once, we don't have to be
so pessimistic to accumulate all possible fuzziness together, and
expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$ to happen.

The Choquet integral has many desirable properties. For example, it
can be represented as a weighted average over all minimum and maximum
of the random variable. Most importantly, the Choquet integral has
the same range as all expectation value in the core.

@@

Before discussing the measurement process and their manifestations
with quantum IVPMs, we first review various notations brought forward
from conventional quantum theory. Assume that a physical system is
represented by a density matrix~$\rho$, and that we wish to measure
a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectrum decomposition is given by
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}\ .
\end{equation}
where $P_{i}$ is the projector onto the eigenspace of the eigenvalue~$\lambda_{i}$.
Then the Born rule of CQT tells us that the expectation value of the
observable~$\mathbf{O}$ is given by
\begin{equation}
\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\Tr\left(\rho P_{i}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .
\end{equation}

>>>>

There are various different integral defined for IVPMs, and the most
famous one is called the Choquet integral~\cite{Choquet1954,GilboaSchmeidler1994,Grabisch2016}.
Let $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$ be a random variable
with $x_{1}\le x_{2}\le\ldots\le x_{N-1}\le x_{N}$ and $\bar{\mu}:\events\rightarrow\mathscr{I}$
a classical IVPM such that $l:\events\rightarrow\left[0,1\right]$
and $r:\events\rightarrow\left[0,1\right]$ are the left-end and the
right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[l\left(E\right),r\left(E\right)\right]$.
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{i=1}^{N}x_{i}\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\textrm{ ,}\label{eq:interval-expectation}
\end{equation}
where multiplying a negative number switching the left and right end
of an interval 
\begin{equation} 
x[l,r]=\cases{ 
[xl,xr] & for $x\ge0$ ;\\
[xr,xl] & for $x\le0$ .
}
\end{equation}
Similar to equation~(\ref{eq:expectation}), equation~(\ref{eq:interval-expectation})
can be considered as weighted average of the possible outcomes of
$X$ as well, despite the ``weight''
\[
\left[l\left(\bigcup_{j\ge i}E_{j}\right)-l\left(\bigcup_{j\ge i+1}E_{j}\right),r\left(\bigcup_{j\ge i}E_{j}\right)-r\left(\bigcup_{j\ge i+1}E_{j}\right)\right]\subseteq\left[l\left(E_{i}\right),r\left(E_{i}\right)\right]=\bar{\mu}\left(E_{i}\right)
\]
is tighter than the interval-valued probability of the corresponding
event. Since only one event can happen at once, we don't have to be
so pessimistic to accumulate all possible fuzziness together, and
expect $\sum_{i=1}^{N}x_{i}\bar{\mu}\left(E_{i}\right)$ to happen.

The Choquet integral has many desirable properties. For example, it
has the same range as all expectation value in the core.

@@

Before discussing quantum IVPMs, we first review various notations
brought forward from conventional quantum theory. Assume that a physical
system is represented by a density matrix~$\rho$, and that we wish
to measure a physical quantity~${\cal O}$ of this system, with corresponding
observable~$\mathbf{O}$, whose spectrum decomposition is given by
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$, where $P_{i}$ is the
projector onto the eigenspace of the eigenvalue~$\lambda_{i}$. Then,
the Born rule of CQT tells us that the expectation value of the observable~$\mathbf{O}$
is given by
\begin{equation}
\Tr\left(\rho\mathbf{O}\right)=\sum_{i=1}^{N}\lambda_{i}\Tr\left(\rho P_{i}\right)=\sum_{i=1}^{N}\lambda_{i}\mu_{\rho}^{\mathrm{B}}\left(P_{i}\right)\ .
\end{equation}
